Part II

### 2021-05-26 PartII.tex
test

>>>>

\subsection{$E_n$ algebras from topological field theories}

Although our focus in this paper is on holomorphic field theories and factorization algebras,
it might be helpful to describe some motivating results about topological field theories and factorization algebras.
Elliott and Safronov have \owen{not sure how much to say here, but I'm going to take a stab at writing a synoptic theorem}

If one examines theories like Chern-Simons theory on $\RR^3$ or the Poisson $\sigma$-model on $\RR^2$, 
one discovers a general format for constructing theories that was formalized by \cite{AKSZ}.
In a nutshell, the field theory is factored into two parts: 
the de Rham complex of the source or ``spacetime'' manifold, 
and a Lie algebra-type object encoding a gauge Lie algebra or a ``target'' for a $\sigma$-model.

\begin{dfn}
A classical {\em AKSZ-type theory} on $\RR^d$ is a determined by an $L_\infty$-algebra $\fg$ equipped with a cyclic pairing $\langle-,-\rangle$ of degree $3-d$.
Its {\em equation of motion} is the Maurer-Cartan equation 
\[
0 = \d A + \frac{1}{2} [A,A] + \frac{1}{3!}[A,A,A]_3 + \cdots = \sum_{k=1}^\infty \frac{1}{k!} [A, \ldots, A]_k
\]
of the $L_\infty$ algebra $\Omega^*(\RR^d) \otimes \fg$ with $k$-ary brackets $[-]_k$.
The {\em action functional} is the expression
\[
S(A) = \int_{\RR^d} \sum_{k=1}^\infty \frac{1}{{k+1}!} \langle A, [A, \ldots, A]_k \rangle
\]
\end{dfn}

Ordinary Chern-Simons theory on $\RR^3$ arises from taking $\fg$ to be a semisimple Lie algebra and a choice of invariant pairing.
In that case, and using $\Tr$ to denote the pairing, the action functional is the familiar
\[
S(A) = \int_{\RR^3}  \frac{1}{2}\Tr ( A, \d A ) + \frac{1}{3!} \Tr( A, [A, A])
\]
and the equation of motion asks for connections with zero curvature.

Many other theories can be expressed in this style, and we suggest \owen{lots of papers} for examples.
Elliott and Safronov characterize and exhibit topological twists of supersymmetric theories as AKSZ-type theories.

\begin{thm}[\cite{CG2;ElliottSafronov}]
For a classical AKSZ-type theory on $\RR^d$, the observables 
\[
\Obs^{cl}(U) = \clie^*(\Omega^*(U) \otimes \fg)
\]
form a locally constant factorization algebra and hence determine an $E_d$ algebra~$\cA^{cl}$.
A quantization, if it exists, determines a deformation $\cA^q$ of this $E_d$ algebra.

Given a homotopical trivialization of the action of $SO(d)$, then $\cA^q$ is a framed $E_d$ algebra.
More generally, given a map of Lie groups $G \to SO(d)$ and a compatible $G$-action on the theory, a homotopical trivialization of this action on the quantum theory equips $\cA^q$ with the structure of a $G$-framed $E_d$ algebra.
\end{thm}

Scheimbauer's thesis then provides a functorial field theory in the sense of Atiyah, Segal, and Lurie.

\begin{thm}
Given a homotopically $SO(d)$-trivial quantization of a classical AKSZ theory on $\RR^d$, 
factorization homology of the quantum observables 
\[
\int_{-} \cA^q : {\rm Bord}^{or}_d \to {\rm Alg}^{or}_d
\]
determines a fully extended oriented $d$-dimensional field theory with values in a higher Morita $(\infty,d)$-category of framed $E_d$ algebras.
\end{thm}

\owen{I should double-check whether Claudia or someone else has described this oriented Morita category ...}
